### 2023-04-17 README.Rmd
Started extracting jurisdiction specific functions out of aMSE.
Generalized save-hsargs to allow for data.frames

>>>>

* 2023-04-17 aMSE 0.1.2 Amended save_hsargs so it can handle data.frame within hsargs.

* 2023-04-12 aMSE 0.1.1 Started generalizing the outputs from aMSE by beginning to separate functions that relate to specific jurisdiction outputs into a separate R package (in Tasmania it is currently called aMSEExtra).
